---
title: "Titel der Arbeit"
subtitle: "Untertitel der Arbeit"
author:
  - name: Ludwig Wittgenstein
    affiliations:
      address: Hauptstraße 10
      city: Mainz
      country: Germany
      postal-code: 12345
    email: name@students.uni-mainz.de
city-of-birth: Wien
date: today
date-format: "YYYY"
sva: Prof. Dr. Kai Arzheimer
svb: Prof. Dr. Claudia Landwehr
student-number: 1234567
format:
  ed-master-pdf: default
---

```{r}
#| label: setup-packages

library(knitr)
library(kableExtra)
library(ggplot2)
```

\pagebreak

\pagenumbering{roman}

# German Summary{.unnumbered}

\begingroup
\fontsize{11pt}{11pt}\selectfont
\begin{otherlanguage}{ngerman}
\lipsum[1-3]
\end{otherlanguage}
\endgroup
\pagebreak

\tableofcontents

\pagebreak

\listoffigures

\pagebreak

\listoftables

\pagebreak

\pagenumbering{arabic}

# Introduction {#sec-A}

\lettrine[lines=2, findent=3pt, nindent=0pt]{F}{irst} \lipsum[5-9]

::: {#fig-example fig-pos="t"}

::: {.figure-content}

```{r}
#| label: example-figure
#| fig-height: 3.5

data.frame(
  a = c(1, 5, 2, 5, 6),
  b = c(5, 2, 43, 5, 1)
) |>
  ggplot(aes(a, b)) +
    geom_point()
```

:::

\floatfoot{\textbf{Note:} Own illustration.}

Example Figure

:::


\lipsum[12-14]

::: {#tbl-example}

\begingroup
\fontsize{10pt}{10pt}\selectfont

::: {.table-content}
```{r}
#| label: table-example

data.frame(
        col1 = c(
            "Lorem",
            "ipsum",
            "dolor"
        ),
        col2 = c(
            "sit",
            "amet",
            "consectetur"
        ),
        col3 = c(
            "adipisici",
            "elit",
            "sed"
        )
    ) |>
    kable(
        col.names = c("Column 1", "Column 2", "Column 3"),
        align = c("l", "l", "r"),
        booktabs = TRUE,
        linesep = ""
    ) |>
    kable_styling(full_width = TRUE) |>
    row_spec(0, bold = TRUE)
```

\endgroup

:::
\floatfoot{\textbf{Note:} Table created for illustration purposes.}

Example Table

:::

\lipsum[15-16]

# References {.unnumbered}

\chaptermark{References}

Place your refs here using a div according to the description [here](https://quarto.org/docs/authoring/footnotes-and-citations.html#bibliography-generation).

\appendix

# Appendix {.unnumbered}

\chaptermark{Appendix}
\renewcommand{\thetable}{A\arabic{table}}
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}
\setcounter{table}{0}

::: {#fig-appendix fig-pos="h"}

::: {.figure-content}

```{r}
#| label: appendix-figure
#| fig-height: 3.5

data.frame(
  a = c(1, 5, 2, 5, 6),
  b = c(5, 2, 43, 5, 1)
) |>
  ggplot(aes(a, b)) +
    geom_point()
```

:::

\floatfoot{\textbf{Note:} Own illustration for the appendix.}

Appendix Figure

:::